## Evolutionary History of Siphonophore Biology

### 2017-02-21 character_coding/CharacterEvolution.Rmd
included phylolm alternative and knitted

#Packages BIO-PHYLO
library('vegan')
library("ape")
library("ggtree")
library("phangorn")
library("phytools")
library("picante")
library("geiger")
library("phylobase")
library("fields")
library("adephylo")
library("geomorph")

@@

>>>>

#Packages BIO-PHYLO
library('vegan')
library("ape")
library("ggtree")
library("phangorn")
library("phytools")
library("picante")
library("geiger")
library("phylobase")
library("fields")
library("adephylo")
library("geomorph")
library("phylolm")

@@

###PGLS
```{r pgls_depth_sex, echo=F, message=F, warning=F}
dp_sex <- dpruned_data$Sex
dp_sex = as.numeric(dp_sex)
names(dp_sex) = names(depth_median)
dp_sex[dp_sex==2] = 0        # 0 = Monoecious, 1 = Dioecious
#Vx <- Vy <- Cxy <- rep(0,length(dpruned_tree$tip.label))
#pgls.Ives(dpruned_tree, dp_sex, depth_median, Vx, Vy, Cxy)
pGLS = pgls.Ives(dpruned_tree, rep(dp_sex,3), rep(depth_median,3))
phylolm(depth_median~dp_sex,data=as.data.frame(cbind(depth_median,dp_sex)),phy=dpruned_tree,model="BM",measurement_error=TRUE,boot=100)
gls(dp_sex ~ depth_median)
```
